---
title: "Members of the 3i consortium"
date: "26 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, fig.width = 9.5}
library(leaflet)

KCL_icon <- makeIcon(
  iconUrl = "https://alumni.kcl.ac.uk/image/2015-site/KCL_boxed_redcmyk_A4-002-3.gif",
  iconWidth = 31*223/170, iconHeight = 31,
  iconAnchorX = 31*223/170/2, iconAnchorY = 16)

Oxford_icon <- makeIcon(
  iconUrl = "https://upload.wikimedia.org/wikipedia/en/thumb/2/2f/University_of_Oxford.svg/1280px-University_of_Oxford.svg.png",
  iconWidth = 31*320/98, iconHeight = 31,
  iconAnchorX = 31*320/98/2, iconAnchorY = 16)

Cambridge_icon <- makeIcon(
  iconUrl = "https://seeklogo.com/images/U/university-of-cambridge-logo-E6ED593FBF-seeklogo.com.png",
  iconWidth = 31*260/300, iconHeight = 31,
  iconAnchorX = 31*260/300/2, iconAnchorY = 16)

Manchester_icon <- makeIcon(
  iconUrl = "https://upload.wikimedia.org/wikipedia/en/thumb/7/72/UniOfManchesterLogo.svg/1280px-UniOfManchesterLogo.svg.png",
  iconWidth = 31*320/135, iconHeight = 31,
  iconAnchorX = 31*320/135/2, iconAnchorY = 16)

WTSI_icon <- makeIcon(
  iconUrl = "https://jobs.newscientist.com/getasset/f487d204-be75-45b8-b95c-7bd776dbfd25/",
  iconWidth = 31*360/180, iconHeight = 31,
  iconAnchorX = 31*360/180/2, iconAnchorY = 16)

AECOM_icon <- makeIcon(
  iconUrl = "https://upload.wikimedia.org/wikipedia/en/thumb/a/a3/Albert_Einstein_College_of_Medicine.svg/1280px-Albert_Einstein_College_of_Medicine.svg.png",
  iconWidth = 31*320/97, iconHeight = 31,
  iconAnchorX = 31*320/97/2, iconAnchorY = 16)

Imperial_icon <- makeIcon(
  iconUrl = "http://wwwf.imperial.ac.uk/~bm508/Imperial.jpg",
  iconWidth = 31*364/140, iconHeight = 31,
  iconAnchorX = 31*364/140/2, iconAnchorY = 16)

threei_map <- leaflet() %>% addTiles() %>% setView(lat=52.472044, lng=-4.938739, zoom=6)

threei_map <- threei_map %>%
      addMarkers(threei_map, lat=51.502857, lng=-0.087596, icon = KCL_icon, popup = paste(sep = "<br/>", "<b><a                href='https://www.kcl.ac.uk/lsm/research/divisions/diiid/departments/immunobiology/research/hayday/index.aspx'>Adrian Hayday</a></b>", "Department of Immunobiology", "King's College London")) %>%
  addMarkers(threei_map, lat=51.759434, lng=-1.251551, icon = Oxford_icon, popup = paste(sep = "<br/>", "<b><a href='http://users.path.ox.ac.uk/~ciu/kmgroup/index.htm'>Kevin Maloy</a></b>", "Sir William Dunn School of Pathology","University of Oxford")) %>%
  addMarkers(threei_map, lat=51.752292, lng=-1.216062, icon = Oxford_icon, popup = paste(sep = "<br/>", "<b><a href='https://www.ndm.ox.ac.uk/principal-investigators/researcher/richard-cornall#research'>Richard Cornall</a></b>", "Centre for Cellular and Molecular Physiology","University of Oxford")) %>%
  addMarkers(threei_map, lat=52.176461, lng=0.141759, icon = Cambridge_icon, popup = paste(sep = "<br/>", "<b><a href='https://www.cimr.cam.ac.uk/research/principal-investigators/principal-investigators-a-h/griffiths'>Gillian Griffiths</a></b>", "Cambridge Institute for Medical Research","University of Cambridge")) %>%
  addMarkers(threei_map, lat=53.464997, lng=-2.227588, icon = Manchester_icon, popup = paste(sep = "<br/>", "<b><a href='https://www.research.manchester.ac.uk/portal/en/researchers/richard-grencis(8663ef93-0d33-4679-a0d9-5924ad2598cb).html'>Richard Grencis</a></b>", "Division of Infection, Immunity & Respiratory Medicine","University of Manchester")) %>%
  addMarkers(threei_map, lat=52.079565, lng=0.185555, icon = WTSI_icon, popup = paste(sep = "<br/>", "<b><a href='http://www.sanger.ac.uk/people/directory/adams-david'>David Adams</a></b>", "<b><a href='http://www.sanger.ac.uk/people/directory/dougan-gordon'>Gordon Dougan</a></b>", "Wellcome Trust Sanger Institute")) %>%
  addMarkers(threei_map, lat=52.764889, lng=-12.433139 , icon = AECOM_icon, popup = paste(sep = "<br/>", "<b><a href='http://www.einstein.yu.edu/faculty/6703/william-jacobs-jr/'>William Jacobs Jr</a></b>", "Department of Micropbiology and Immunology","Albert Einstein College of Medicine")) %>%
  addMarkers(threei_map, lat=51.497612, lng=-0.176308 , icon = Imperial_icon, popup = paste(sep = "<br/>", "<b><a href='https://www.imperial.ac.uk/people/c.lloyd'>Clare Lloyd</a></b>", "National Heart and Lung Institute","Imperial College London"))
  
threei_map

```

### The 3i project is building an encyclopaedia of immunological gene functions to advance basic and translational research

The Infection and Immunity Immunophenotyping (3i) consortium conducts a high-throughput immunological phenotyping of over 500 knockout mouse lines generated by the Wellcome Trust Sanger Institute (WTSI). Funded by the Wellcome Trust and led by King's College London, the consortium includes partners from WTSI, Imperial College, Albert Einstein College of Medicine, and the Universities of Oxford, Cambridge, and Manchester.
